Brownian Dynein Model

### 2016-04-14 latex/paper.tex
we discovered a mistake in "far" angle handling, now partially documented

\begin{figure}
  \includegraphics[width=\columnwidth]{../figures/code-bothbound.png}
  \caption{Angles used in both-bound case.}\label{fig:bothbound}
\end{figure}

@@

\subsection{Farbound coordinates}
The farbound coordinates are defined identically to the nearbound coordinates, except
Ln and Lf coordinates switch places.

>>>>

\begin{figure}
  \includegraphics[width=\columnwidth]{../figures/code-bothbound}
  \caption{Angles used in both-bound case.}\label{fig:bothbound}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{../figures/similar-bothbound}
  \caption{Angles used in both-bound case.}\label{fig:similar}
\end{figure}

\subsection{Farbound coordinates}
The farbound coordinates are defined similarly (but not quite) to the nearbound coordinates, with
$L_n$ and $L_f$ coordinates switched places.
\begin{align}
  \cos\theta_f &= -\frac{L^2 + L_f^2 - L_n^2}{2L L_f} \\
  \sin\theta_{f} &= \sqrt{1 - \cos^2\theta_{f}} \\
  \cos\theta_{fs} &= \frac{L_s^2 + L_f^2 - L_t^2}{2L_s L_f} \\
  \sin\theta_{fs} &=
  \begin{cases}
    +\sqrt{1 - \cos^2\theta_{fs}} & \theta_{fm} < \pi \\
    -\sqrt{1 - \cos^2\theta_{fs}} & \theta_{fm} > \pi
  \end{cases}
\end{align}
